Treatment effects

### 2017-03-09 ScaleUp/ITT_ATT.tex
versión final de resultados_ATT_ITT, results actualizado

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amscd}
\usepackage{hyperref}
\usepackage{enumerate}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage{amsthm}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{tikz}
\usepackage{color} %red, green, blue, yellow, cyan, magenta, black, white
\usepackage{fullpage}
\usepackage{mathtools}
\usepackage{booktabs}
\usepackage{longtable}

@@

\section{\Huge{Some Summary Statistics}}

@@

@@

\begin{figure}[H]
\label{diff}
\begin{center}
\includegraphics[width=\textwidth]{./Figures/belief.pdf}
\end{center}
{\footnotesize \textit{The histograms are trimmed at the 90 percentile in the case for amount. Width of bins are \$50,000 pesos for the case of amount and 10\% for the case of probability.}}
\end{figure}

\begin{figure}[H]
\label{update}
\begin{center}
\includegraphics[width=\textwidth]{./Figures/update_belief.pdf}
\end{center}
{\footnotesize \textit{The histograms measures the update in relative terms. Width of bins is 0.25 }}
\end{figure}

@@

>>>>

\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amscd}
\usepackage{hyperref}
\usepackage{enumerate}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage{amsthm}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{lscape}
\usepackage{tikz}
\usepackage{color} %red, green, blue, yellow, cyan, magenta, black, white
\usepackage{fullpage}
\usepackage{mathtools}
\usepackage{booktabs}
\usepackage{longtable}

@@

\section{Some Summary Statistics}

@@

\begin{center}
\scriptsize{\input{\folder/TAB_survey.tex}}
\end{center}

@@

\begin{figure}[H]
\label{diff}
\begin{center}
\includegraphics[width=\textwidth]{./Figures/belief.pdf}
\end{center}
{\footnotesize \textit{The histograms are trimmed at the 75 percentile in the case for amount. Width of bins are \$30,000 pesos for the case of amount and 10\% for the case of probability.}}
\end{figure}

\begin{figure}[H]
\label{update}
\begin{center}
\includegraphics[width=\textwidth]{./Figures/update_belief.pdf}
\end{center}
{\footnotesize \textit{The histograms measures the update in relative terms. It displays the distribution from the percentile 5 to 95.}}
\end{figure}

@@

\section{ITT and ATT regressions}

\begin{landscape}
\subsection*{ITT and Second Stage ATT}

\begin{center}
\scriptsize{\input{\folder/ITT_ATT.tex}}
\end{center}

\end{landscape}

\subsection*{First Stage for ATT regressions}

\begin{center}
\scriptsize{\input{\folder/FS_ATT.tex}}
\end{center}

\section{Take up regression (calculator and survey)}

\begin{center}
\scriptsize{\input{\folder/Take_up.tex}}
\end{center}
